gtsummary Reviewer Responses

### 2021-04-10 reviewer_responses/gtsummary_review_2021-03-23.Rmd
updates

---
title: "gtsummary Reviewer Responses"
author: "Dan Sjoberg, Karissa Whiting, Mike Curry"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    theme: sandstone
    toc: yes
    toc_float: yes
    number_sections: true
editor_options: 
  chunk_output_type: console
---

@@

> We agree that a short section in the paper mentioning capabilities of other similar table making packages will help contextualize gtsummary's value. We have added this in the revised paper.

@@

@@

2. I’m not sure I understand the motivation for the table customization functions (e.g., bold_levels). Isn’t the whole point of building a package on top of gt that we can leverage its functions directly?

> While the package allows users to easily leverage gt customization, Knowledge of gt isn’t necessary to use the package. We’ve included some helper functions that make the most commonly needed customizations readily available to users who may not be familiar with {gt}, or may want to use any of the other print engines. Having the customization functions for these most common everyday customization tasks allows the users to make these customizations regardless of the print engine or output format they want to use, and customizations remain reproducible, even if they decide to switch print engine or output format.

> Most importantly, these functions helps the average users who may not be familiar with the internals of the package get. For example, to bold using {gt} functions, you have to have some knowledge of internal structure of gtsummary tables to select the correct columns and rows to customize.

```{r}
# include example?
```

@@

> {gtsummary} currently has over XX tests. As noted, many of these tests check for specific warnings/messages, however many of these are looking for specific targeted warnings/messages that also test functionality, and there are still a considerable amount that check for expected returned values, etc.

> We are hesitant to add additional tests due to runtime/computational load, but will audit current tests and aim to change over some expect_error(), expect_warning() tests to more targeted tests for specific output values in the future.

@@

> Although you can't currently adjust the default cutoff, tidyselect helper functions and the `type`  argument make it very easy to specify what type you want your variables to be.

@@

> tbl_summary() works with tidyselect functions, so you can specify all with the following:

```{r}
trial %>% 
  select(age, marker, ttdeath) %>%
  tbl_summary(digits = everything() ~ 2)

@@

> We added frequency sorting and alpha numeric for convenience, but we suggest to users that any variable or dataframe transformation should be done before passing tables to tbl_summary().

> For variable levels you can use `forcats::fct_relevel()`

```{r}

> For variable order you can use use `dplyr::select()`

```{r}

@@

> TBD

@@

> TBD

>>>>

---
title: "gtsummary Reviewer Responses"
author: "Daniel Sjoberg, Karissa Whiting, Mike Curry"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    theme: sandstone
    toc: yes
    toc_float: yes
    number_sections: true
editor_options: 
  chunk_output_type: console
---

@@

> We agree that a section in the paper mentioning capabilities of other similar table making packages will help contextualize gtsummary's value. We have added this in the revised paper.

@@

> The original submission did not make reference specically to the availability of LaTeX output. We've added text to the *Print Engine* section of the manuscript explicicty listing the output options, including LaTeX.

@@

2. I’m not sure I understand the motivation for the table customization functions (e.g., bold_levels). Isn’t the whole point of building a package on top of {gt} that we can leverage its functions directly?

> The reviewer raises a great point. One of the great features of gtsummary is teh accessabitily of every gt function to produce a highly customized table, when needed. We have included functions to assist in common formatting to make them more accessible to users. For example, to re-created the functionality of the `bold_labels()` function, the user would need to pass `as_gt() %>% gt::tab_style(style = gt::cell_text(weight = "bold"), locations = gt::cells_body(columns = gt::vars(label), rows = row_type == "label"))`. The helper function is much easier to read, and moreover, the gt version requires knowledge of hidden columns (e.g. `"row_type"`) to correctly select the label rows. Without these formatting helper functions, most passive users of the package would not have the knowledge to create the formatting on their own.

@@

> As noted by the reviewer, many of the unit tests check for specific error/warnings/messages, which in some cases, may not be considered best practices. The {gtsummary} package, however, currently has 1100 unit tests with hundreds of tests that check for quite specific output. The sum total of the tests, in our opinion, provides great unit testing coverege testing a wide variety of options possible in the package.

@@

> Although you can't currently adjust the default cutoff, tidyselect helper functions and the `type=`  argument make it very easy to specify what type you want your variables to be.

@@

> tbl_summary() works with all tidyselect functions (in addition to tidyselect-like functions exported by {gtsummary}), and you can specify all variables using the `everything()` selector. For example,

```{r}
trial %>% 
  select(age, marker, ttdeath) %>%
  tbl_summary(digits = everything() ~ 2)
```

@@

> The ordering of the variable in `tbl_summary()` aligns with the order the variables appear in the input data frame. To re-arrange the variables, use `select()` before passing the data frame to `tbl_summary()`, e.g. `trial %>% select(age, grade) %>% tbl_summary()`

@@

> Yes! Any function in base R, another package, or user-defined can be used to summarize the continuos data in `tbl_summary()`. The only restriction is the first argument of the function must accept a vector, and return a scalar.

@@

> The terms appear in the same order as regression function. The simplest way to reorder the terms to order them in, for example, the `lm()` call. If for some reason that is not possible, they can be re-ordered after the `tbl_regression()` table has been built using `modify_table_body()` with `dplyr::arrange()`.
